\section{Working Experience}

\datedsubsection{Graduate Research}{June $2021$--Present}{Barcelona (Spain)}
\begin{itemize}
  \item PhD Student at the Barcelona Institute of Global Health (ISGlobal)
  \item Supervisors: Dr. Martine Vrijheid (ISGlobal), Dr. Lea Maitre (ISGlobal)
\end{itemize}


\datedsubsection{Graduate Research}{June $2019$--October $2019$}{Trento (Italy)}
\begin{itemize}
  \item Master thesis at the Bruno Kessler Foundation
  \item Thesis: \textit{Machine Learning for Predictive Drug-Induced Hepatotoxicity}
  \item Supervisors: Dr. Cesare Furlanello (FBK), Dr. Marco Chierici (FBK), Prof. Enrico Domenici (UNITN)
\end{itemize}


\datedsubsection{Graduate Research}{March $2019$--May $2019$}{Heidelberg (Germany)}
\begin{itemize}
  \item Internship at the Heidelberg Institute for Theoretical Studies
  \item Research project: \textit{Machine and Deep Learning for Predictive Unbinding Kinetics of Kinases}
  \item Supervisors: Prof. Rebecca Wade (HITS), Dr. Daria Kokh (HITS), Prof. Raffaello Potestio (UNITN)
\end{itemize}


\datedsubsection{Graduate Research}{October $2016$--May $2017$}{Lugano (Switzerland)}
\begin{itemize}
  \item Student Research Assistant at Università della Svizzera italiana
  \item Research project: \textit{Investigation by Computational Techniques of Channelopaties related to Sodium Channels}
  \item Supervisors: Prof. Vittorio Limongelli, Prof. Daniele Di Marino
\end{itemize}


\datedsubsection{Undergraduate Research}{April $2015$--August $2015$}{Aachen (Germany)}
\begin{itemize}
  \item Internship and Bachelor thesis at RWTH Aachen University
  \item Thesis: \textit{Whole-body PBPK Modeling of Valproic Acid}
  \item Supervisors: Prof. Elena Maestri (UNIPR), Prof. Lars M. Blank (RWTH), Dr. Henrik Cordes (RWTH)
\end{itemize}
